---
title: 'Lab 8: Feature Engineering'
author: "K Arnold & K Westra"
date: "10/23/2020"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
```

## Data

Load data from `modeldata` package.

```{r load-data}
data(ames, package = "modeldata")
ames <- ames %>% 
  filter(Gr_Liv_Area < 4000, Sale_Condition == "Normal") %>% 
  mutate(across(where(is.integer), as.double))
```

Hold out a test set.

```{r train-test-split}
set.seed(10) # Seed the random number generator
ames_split <- initial_split(ames, prop = 2/3) # Split our data randomly
ames_train <- training(ames_split)
ames_test <- testing(ames_split)
```

We'll use one example home from the test set.

```{r example-home}
example_home <- ames_test %>% slice(1)
example_home %>% select(Gr_Liv_Area, Sale_Price)
```

## Recipe

Here we set up the recipe:

```{r prep-recipe}
ames_recipe <- 
  recipe(Sale_Price ~ Gr_Liv_Area + Latitude + Longitude, data = ames_train) %>% 
  #make the scale the SAME for all of these!!!!
  step_range(Gr_Liv_Area, Latitude, Longitude, min = 0, max = 1) %>%
  prep()
ames_recipe %>% summary()
```

Let's look at its output on the training data:

```{r apply-recipe-train}
ames_recipe %>% bake(new_data = ames_train)
```

## Workflow

`workflow` = `recipe` + `model`

```{r workflow}
ames_workflow <- workflow() %>%
  add_model(linear_reg() %>% set_engine("lm")) %>% 
  add_recipe(ames_recipe)
```

Workflows can `fit` and `predict`. First let's `fit` it on our training data...

```{r fit-workflow1-on-train}
fitted_workflow <- fit(ames_workflow, data = ames_train)
```

Now let's see what it predicts for our example home.

```{r predict-workflow1-on-example}
fitted_workflow %>% predict(example_home)
```

Let's peek inside the model.

```{r unscaled-latlong}
fitted_workflow %>% 
  tidy() %>%
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = estimate, y = term)) + geom_col()
```

```{r}
ames_train %>% select(Gr_Liv_Area, Latitude, Longitude) %>% summary()
```


Because these features are on such totally different scalees, if we want a similar effect, we need a huge coefficient.

## Test the model

```{r preprocess-test-data}
fitted_workflow %>%
  pull_workflow_prepped_recipe() %>% 
  bake(new_data = ames_test) %>% #<<
  summary()
```

```{r predict-on-test-data}
fitted_workflow %>%
  predict(ames_test) %>% 
  bind_cols(ames_test) %>% 
  ggplot(aes(x = Sale_Price, y = Sale_Price - .pred)) + geom_point() + geom_smooth()

fitted_workflow %>%
  predict(ames_test) %>% 
  bind_cols(ames_test) %>% 
  ggplot(aes(x = .pred, y = Sale_Price - .pred)) + geom_point() + geom_smooth()
```

## Conditional Logic

Do remodeled homes sell for more?  
From codebook: remodel data = construction date if no remodeling or additions.

```{r}
ames_train_2 <- ames_train %>% 
  mutate(remodeled = case_when(
    Year_Built == Year_Remod_Add ~ "no",
    TRUE                         ~ "yes") %>%
    as_factor()
  )
```


```{r remodeled}
ames_train_2 %>% 
  ggplot(aes(x = Gr_Liv_Area, y = Sale_Price, color = remodeled)) +
  geom_point() +
  geom_smooth(method = "lm")
```

It looks like remodelled homes sell for... less?
Yet correlation ≠ causation, and it might be that somethinng that caused a model also brought about price-lowering things... 

***

#### *AS AN ASIDE:*

```{r sum-as-count}
ames_2 <- ames %>%
  mutate(remodeled = Year_Remod_Add != Year_Built)

ames_2 %>%
  group_by (remodeled) %>%
  summarize(n = n()) %>%
  mutate(proportion = n / sum(n))

ames_2 %>%
  summarize(num_remodeled = sum(remodeled == T),
            Prop_remodeled = mean(remodeled == T))

```

***

Linear model... treating remodelled homes differently from non-remodelled.

**dummy encoding**

essentailly, we just add a term:

Sale_Price =   
   intercept_other  
   + coef_remodeled * (1 if remodeled)  
   + coef_sqft      * Gr_Liv_Area  

(similar to what we did in the aside above!)
A *conditional* intercept.

How to do it:

```{r}
ames_recipe_3 <- 
  recipe(Sale_Price ~ Gr_Liv_Area + remodeled, data = ames_train_2) %>% 
  step_dummy(remodeled) %>%
  # rescalling step:
  #step_range(all_numeric(), -all_outcomes(), min = 0, max = 1) %>% 
  prep()

baked_ames_train <- 
  ames_recipe_3 %>% bake(new_data = ames_train_2)

baked_ames_train %>% head(5) %>% knitr::kable(format = "html")
#having a "remodeled_no" column is unnecessary -- it's just a 0 in our remodeled_yes col!
```

```{r}
ames_model_2 <- linear_reg() %>% set_engine("lm") %>% 
  fit(Sale_Price ~ ., data = baked_ames_train)
ames_model_2 %>% tidy() %>% select(term, estimate) %>% knitr::kable()
```

Sale_Price = 
   22643 
   + -18424.0789 * (1 if remodeled)
   + 109.1132 * Gr_Liv_Area
   
If remodelleed, subtract 18k from price :( otherwise, just keep going.

```{r}
typeof(baked_ames_train$remodeled_yes)
baked_ames_train %>%
  mutate(remodeled_yes = as.factor(remodeled_yes)) %>%
ggplot(aes(x = Gr_Liv_Area, y = Sale_Price, color = remodeled_yes)) +
  geom_point() +
  geom_function(fun = function(x) (22643.4248 - 18424.0789) + 109.1132 * x, color = "blue") +
  geom_function(fun = function(x) 22643.4248 + 109.1132 * x, color = "green")
```

More than 2 options:

```{r}
ames_train %>% count(Bldg_Type) %>% knitr::kable()
ames_recipe_4 <- 
  recipe(Sale_Price ~ Gr_Liv_Area + Bldg_Type, data = ames_train) %>% 
  step_dummy(Bldg_Type) %>%
  #step_range(all_numeric(), -all_outcomes(), min = 0, max = 1) %>%
  prep()
baked_ames_train <- 
  ames_recipe_4 %>% bake(new_data = ames_train_2)
baked_ames_train %>% head(5) %>% knitr::kable(format = "html")
```

Creates 4 columns!
^^ the first isn't included because it's built into the intercept.

The other 4 columns are just used in reference to 

Which one gets treated as base: depends on package.
Statistical inferenece: which condition is being treated as baseline. (this is important to think this through... does one make more sense than the other)

>> ran into this problem w/ CSR data -- homeless was treated as the baseline to which everything else was statistically signifiant.!s


** contrasts w/ baseline!! ** 

**Interpret** as: diff between ____ and [baseline]


```{r, eval=F, include=F}
ggplot(baked_ames_train, aes(x = Gr_Liv_Area, y = Sale_Price, color = Bldg_Type)) +
  geom_point()
  #geom_function(fun = function(x) (22643.4248 - 18424.0789) + 109.1132 * x, color = "blue") +
  #geom_function(fun = function(x) 22643.4248 + 109.1132 * x, color = "green")
```

## Another kind of model: Decision Trees

[see examples](https://cs.calvin.edu/courses/data/202/ka37/slides/w09/w9d2-conditional-logic.html#16) 
and specific [R code and output](https://cs.calvin.edu/courses/data/202/ka37/slides/w09/w9d2-conditional-logic.html#17)

different parts of tree can look @ diff things

**TWO KINDS OF REGRESSION MODELS**

Linear Regression
- To make a prediction: multiply terms by constants, sum it all up  
- Conditional logic by explicitly transforming data to invent special terms  
- Output looks like lines (or curves, if you add $x^2$ terms)  

Decision Tree Regression  
- To make a prediction: follow conditional logic rules (determined automatically from data) to output a number  
- Output looks like stair-steps  
