---
title: 'Lab 8: Feature Engineering'
author: "K Arnold"
date: "10/23/2020"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
```

## Data

Load data from `modeldata` package.

```{r load-data}
data(ames, package = "modeldata")
ames <- ames %>% 
  filter(Gr_Liv_Area < 4000, Sale_Condition == "Normal") %>% 
  mutate(across(where(is.integer), as.double))
```

Hold out a test set.

```{r train-test-split}
set.seed(10) # Seed the random number generator
ames_split <- initial_split(ames, prop = 2/3) # Split our data randomly
ames_train <- training(ames_split)
ames_test <- testing(ames_split)
```

We'll use one example home from the test set.

```{r example-home}
example_home <- ames_test %>% slice(1)
example_home %>% select(Gr_Liv_Area, Sale_Price)
```

## Recipe

Here we set up the recipe:

```{r prep-recipe}
ames_recipe <- 
  recipe(Sale_Price ~ Gr_Liv_Area + Latitude + Longitude, data = ames_train) %>% 
  prep()
ames_recipe %>% summary()
```

Let's look at its output on the training data:

```{r apply-recipe-train}
ames_recipe %>% bake(new_data = ames_train)
```

## Workflow

`workflow` = `recipe` + `model`

```{r workflow}
ames_workflow <- workflow() %>%
  add_model(linear_reg() %>% set_engine("lm")) %>% 
  add_recipe(ames_recipe)
```

Workflows can `fit` and `predict`. First let's `fit` it on our training data...

```{r fit-workflow1-on-train}
fitted_workflow <- fit(ames_workflow, data = ames_train)
```

Now let's see what it predicts for our example home.

```{r predict-workflow1-on-example}
fitted_workflow %>% predict(example_home)
```

Let's peek inside the model.

```{r unscaled-latlong}
fitted_workflow %>% 
  tidy() %>%
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = estimate, y = term)) + geom_col()
```

## Test the model

```{r preprocess-test-data}
fitted_workflow %>%
  pull_workflow_prepped_recipe() %>% 
  bake(new_data = ames_test) %>% #<<
  summary()
```

```{r predict-on-test-data}
fitted_workflow %>%
  predict(ames_test) %>% 
  bind_cols(ames_test) %>% 
  ggplot(aes(x = Sale_Price, y = Sale_Price - .pred)) + geom_point()
```

## Conditional Logic

```{r}
ames_train_2 <- ames_train %>% 
  mutate(remodeled = case_when(
    Year_Built == Year_Remod_Add ~ "no",
    TRUE                         ~ "yes") %>%
    as_factor()
  )
```


```{r remodeled}
ames_train_2 %>% 
  ggplot(aes(x = Gr_Liv_Area, y = Sale_Price, color = remodeled)) +
  geom_point() +
  geom_smooth(method = "lm")
```

